### 2020-04-05 06-examples.tex
piccoli cambi

\subsection{Labelled transition system}
This example is inspired by the example in~\cite{BEMR11}, where
a deterministic transition system is coded in the Reaction System
framework.
Here we consider the minimal deterministic transition system in Figure~\ref{fig:lts}.
%following the reaction system approach, to code it in the reaction system framework, we have to add
%extra labels, as in Figure~\ref{fig:ndlts2}.
\begin{figure}
\[
\xymatrix{
*+[o][F-]{q} \ar@/ ^/[r]^a \ar@(l,u)[]^b &
*+[o][F-]{w} \ar@/^/[l]^b \ar@(r,u)[]_a
}
\]
\caption{Minimal deterministic labelled transition system.}
\label{fig:lts}
\end{figure}
\noindent
In our $c\CNA$ encoding, $q$, $w$, $a$, and $b$ became the $entities$, the context can only provide $a$ and $b$ and the reaction rules are as follows:\\
\[
\begin{array}{cl@{\hspace{1cm}} cl}
1 \ &(\{q,a\},\{w,b\},\{q\}) & 2\ &(\{q,b\},\{w,a\},\{w\})\\
3 \  &(\{w,a\},\{q,b\},\{q\}) & 4\ &(\{w,b\},\{q,a\},\{w\})\\ 
\end{array}
\]
\paragraph{Encoding of the rules}
The encoding of the rules for reactions is  given in a parametric way:
\[
\begin{array}{lcl}
P_n(q,b,w,a,q) & \defeq & \pi_n(q,b,w,a,q).P_n(q,b,w,a,q)  \\
			&& +\\
			&& \sum_{x\in\{\overline{q},\overline{b},w,a\}}\ \pi'_n(x).P_n(q,b,w,a,q)\\
%			&& +\ \pi'(\overline{b}).P_n(q,b,w,a,q)\\
%			&& +\ \pi'(w).P_n(q,b,w,a,q)\\ 
%			&& +\ \pi'(a).P_n(q,b,w,a,q)\\
			\end{array}
			\]
			\noindent
			where
			\[
\begin{array}{lcl}
\pi_n(q,b,w,a,q) &\defeq & \startchain{r_n}\chainedlink{q_i}{\noact}\chainedlink{\noact}{q_o}
                                                    \chainedlink{b_i}{\noact}\chainedlink{\noact}{b_o}
                                                     \chainedlink{\overline{w}_i}{\noact}\chainedlink{\noact}{\overline{w}_o}
					        \chainedlink{\overline{a}_i}{\noact}\chainedlink{\noact}{\overline{a}_o}
					        \chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}
					        \chainedlink{\widetilde{q}_i}{\noact}\chainedlink{\noact}{\widetilde{q}_o}
			\chainend{p_{n+1}}\\
\pi'_n(x) &\defeq &  \startchain{r_n}\chainedlink{x_i}{\noact}\chainedlink{\noact}{x_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}} 
% \ + \   \startchain{r_n}\chainedlink{w_i}{\noact}\chainedlink{\noact}{w_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) \\
%			&&+\\
%			&& \startchain{r_n}\chainedlink{\overline{b}_i}{\noact}\chainedlink{\noact}{\overline{b}_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}\chainend{p_{n+1}}.P_n(q,b,w,a,q) \ + \  \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) 
\end{array}
\]
\noindent
Then we have 
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl  }
P_1 & \defeq & P_1(q,a,w,b,q) & P_3 & \defeq & P_3(w,a,q,b,w)  \\
P_2 & \defeq & P_2(q,b,w,a,w) &P_4 & \defeq & P_4(w,b,q,a,q) 
\end{array}
\]
\noindent
and we put, as usual,
%$r_1 = \silent$, 
$r_5 = \mathit{cxt}$ and  $p_5 = \silent$.

@@

The encoding of the rules for reactions is  given in a parametric way:
\[
\begin{array}{lcl}
P_n(a,G,C,T) & \defeq &\pi_n(a,G,C,T).P_n(a,G,C,T)  \\
				&& +\\
			&&\sum_{x\in \{a,G,C\}} \pi'_n(x).P_n(a,G,C,T)
\end{array}
\]
where
\[
\begin{array}{lcl}
\pi_n(a,G,C,T) & \defeq & \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}
                                                    \chainedlink{G_i}{\noact}\chainedlink{\noact}{G_o}
                                                     \chainedlink{\overline{C}_i}{\noact}\chainedlink{\noact}{\overline{C}_o}
					        \chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}
					        \chainedlink{\widetilde{T}_i}{\noact}\chainedlink{\noact}{\widetilde{T}_o}
			\chainend{p_{n+1}}\\
\pi'_n(x) &\defeq &  \startchain{r_n}\chainedlink{x_i}{\noact}\chainedlink{\noact}{x_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}} 
% \ + \   \startchain{r_n}\chainedlink{w_i}{\noact}\chainedlink{\noact}{w_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) \\
%			&&+\\
%			&& \startchain{r_n}\chainedlink{\overline{b}_i}{\noact}\chainedlink{\noact}{\overline{b}_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}\chainend{p_{n+1}}.P_n(q,b,w,a,q) \ + \  \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) 
\end{array}
\]
\noindent
Then we have 
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl }
P_1 & \defeq & P_1(a,G,C,T) &   P_2 & \defeq & P_2(a,C,G,T') &   P_3 & \defeq & P_3(F,T,T',C)  \\
\end{array}
\]
\[
\begin{array}{lcl}
P_4 & \defeq &\startchain{r_4}\chainedlink{T'_i}{\noact}\chainedlink{\noact}{T'_o}
                                                     \chainedlink{\overline{F}_i}{\noact}\chainedlink{\noact}{\overline{F}_o}
					        \chainedlink{\mathit{cxt}}{\noact}\chainedlink{\noact}{p_4}
					        \chainedlink{\widetilde{G}_i}{\noact}\chainedlink{\noact}{\widetilde{G}_o}
			\chainend{\silent}.P_4  \\
				&& +\\
&&\startchain{r_4}\chainedlink{\overline{T'}_i}{\noact}\chainedlink{\noact}{\overline{T'}_o}\chainedlink{cxt}{\noact}\chainedlink{\noact}{p_4} \chainend{\silent}.P_4 \ +\  \startchain{r_4}\chainedlink{F_i}{\noact}\chainedlink{\noact}{F_o}\chainedlink{\mathit{cxt}}{\noact}\chainedlink{\noact}{p_4} \chainend{\silent}.P_4
\end{array}
\]
\noindent
%and we put $r_1 = \silent$.

@@

Here, the entities $T$ and $T'$ that can be produced by the reactions and that are not provided by the context:
\[
\begin{array}{lcllcl}
P (T,\widetilde{T})&\defeq & \sum_{h=0}^1 (\startchain{T_i}\chainedlink{T_o}{\noact}\chainend{\noact})^h\ \link{\widetilde{T}_i}{\widetilde{T}_o}.P (T,\widetilde{T})
& +  && \link{T_i}{T_o}.P (\overline{T},\widetilde{T}) \\
%\overline{P} (q)&\defeq &  \sum_{h=0}^1 (\startchain{\overline{T}_i}\chainedlink{\overline{T}_o}{\noact}\chainend{\noact})^h\link{\widetilde{T}_i}{\widetilde{T}_o}.P(q)\\
%&& + & && +\\
%&& \link{T_i}{T_o}.\overline{P}(T) &
%&& \link{\overline{T}_i}{\overline{T}_o}.\overline{P}(T)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl}
P_T & \defeq & P(T,\widetilde{T})& \overline{P}_T & \defeq & P(\overline{T},\widetilde{T}) & P_{T'}& \defeq & P(T',\widetilde{T'}) & \\
\overline{P}_{T',\widetilde{T'}}& \defeq & P(\overline{T'},\widetilde{T'})\\\
\end{array}
\]
Here, the entities that can be produced by the reactions and that can be  provided by the context:
\[
\begin{array}{lcl @{\hspace{1cm}}lcl}
P(C,\widehat{C},\underline{C},\widetilde{C}) & \defeq &  \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\widehat{C}_i}{\widehat{C}_o} (\startchain{\noact}\chainedlink{\noact}{\widetilde{C}_i}\chainend{\widetilde{C}_o})^h.   P(C,\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
&& \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o}.P(\overline{C},\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
 && \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o} \startchain{\noact}\chainedlink{\noact}{\widehat{C}_i}\chainend{\widehat{C}_o}.   P(C,\widehat{C},\underline{C},\widetilde{C}) \\
 %&  \overline{E} (a)&\defeq & \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\widehat{a}_i}{\widehat{a}_o}.E(a)\\
%&&  &  && +\\
%&& 
%&
%&& \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\underline{a}_i}{\underline{a}_o}.\overline{E}(q)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{1cm}}lcl@{\hspace{0.4cm}}lcl@{\hspace{0.4cm}}lcl}
P_C & \defeq &  P(C,\widehat{C},\underline{C},\widetilde{C})&  P_G& \defeq &   P(G,\widehat{G},\underline{G},\widetilde{G}) \\
\overline{P}_C & \defeq &  P(\overline{C},\widehat{C},\underline{C},\widetilde{C}) & 
\overline{P}_G& \defeq &   P(\overline{G},\widehat{G},\underline{G},\widetilde{G})\\
\end{array}
\]

Here, the encoding of the entity $F$ that can be provided by the context:
\[
\begin{array}{lcllcl}
P_F&\defeq & \sum_{h=0}^1 (\startchain{F_i}\chainedlink{F_o}{\noact}\chainend{\noact})^h\ \link{\widehat{F}_i}{\widehat{F}_o}.P_F
& +  && \sum_{h=0}^1 (\startchain{F_i}\chainedlink{F_o}{\noact}\chainend{\noact})^h. \link{\underline{F}_i}{\underline{F}_o}.\overline{P}_F \\
\overline{P}_F&\defeq & \sum_{h=0}^1 (\startchain{\overline{F}_i}\chainedlink{\overline{F}_o}{\noact}\chainend{\noact})^h\ \link{\widehat{F}_i}{\widehat{F}_o}.P_F
& +  && \sum_{h=0}^1 (\startchain{\overline{F}_i}\chainedlink{\overline{F}_o}{\noact}\chainend{\noact})^h. \link{\underline{F}_i}{\underline{F}_o}.\overline{P}_F \\
%\overline{P} (q)&\defeq &  \sum_{h=0}^1 (\startchain{\overline{T}_i}\chainedlink{\overline{T}_o}{\noact}\chainend{\noact})^h\link{\widetilde{T}_i}{\widetilde{T}_o}.P(q)\\
%&& + & && +\\
%&& \link{T_i}{T_o}.\overline{P}(T) &
%&& \link{\overline{T}_i}{\overline{T}_o}.\overline{P}(T)\\
\end{array}
\]

>>>>

\subsection{Labelled transition system}
This example is inspired by the example in~\cite{BEMR11}, where
a deterministic transition system is coded in the Reaction System
framework.
Here we consider the minimal deterministic transition system in Figure~\ref{fig:lts}.
%following the reaction system approach, to code it in the reaction system framework, we have to add
%extra labels, as in Figure~\ref{fig:ndlts2}.
\begin{figure}
\[
\xymatrix{
*+[o][F-]{q} \ar@/ ^/[r]^a \ar@(l,u)[]^b &
*+[o][F-]{w} \ar@/^/[l]^b \ar@(r,u)[]_a
}
\]
\caption{Minimal deterministic labelled transition system.}
\label{fig:lts}
\end{figure}
\noindent
In our $c\CNA$ encoding, $q$, $w$, $a$, and $b$ became the $entities$, the context can only provide $a$ and $b$ and the reaction rules are as follows:\\
\[
\begin{array}{cl@{\hspace{1cm}} cl}
1 \ &(\{q,a\},\{w,b\},\{q\}) & 2\ &(\{q,b\},\{w,a\},\{w\})\\
3 \  &(\{w,a\},\{q,b\},\{q\}) & 4\ &(\{w,b\},\{q,a\},\{w\})\\ 
\end{array}
\]
\paragraph{Encoding of the rules}
The encoding of the rules for reactions is  given in a parametric way:
\[
\begin{array}{lcl}
P_n(q,b,w,a,q) & \defeq & \pi_n(q,b,w,a,q).P_n(q,b,w,a,q)  \\
			&& +\\
			&& \sum_{x\in\{\overline{q},\overline{b},w,a\}}\ \pi'_n(x).P_n(q,b,w,a,q)\\
%			&& +\ \pi'(\overline{b}).P_n(q,b,w,a,q)\\
%			&& +\ \pi'(w).P_n(q,b,w,a,q)\\ 
%			&& +\ \pi'(a).P_n(q,b,w,a,q)\\
			\end{array}
			\]
			\noindent
			where
			\[
\begin{array}{lcl}
\pi_n(q,b,w,a,q) &\defeq & \startchain{r_n}\chainedlink{q_i}{\noact}\chainedlink{\noact}{q_o}
                                                    \chainedlink{b_i}{\noact}\chainedlink{\noact}{b_o}
                                                     \chainedlink{\overline{w}_i}{\noact}\chainedlink{\noact}{\overline{w}_o}
					        \chainedlink{\overline{a}_i}{\noact}\chainedlink{\noact}{\overline{a}_o}
					        \chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}
					        \chainedlink{\widetilde{q}_i}{\noact}\chainedlink{\noact}{\widetilde{q}_o}
			\chainend{p_{n+1}}\\[6pt]
\pi'_n(x) &\defeq &  \startchain{r_n}\chainedlink{x_i}{\noact}\chainedlink{\noact}{x_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}} 
% \ + \   \startchain{r_n}\chainedlink{w_i}{\noact}\chainedlink{\noact}{w_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) \\
%			&&+\\
%			&& \startchain{r_n}\chainedlink{\overline{b}_i}{\noact}\chainedlink{\noact}{\overline{b}_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}\chainend{p_{n+1}}.P_n(q,b,w,a,q) \ + \  \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) 
\end{array}
\]
\noindent
Then we have 
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl  }
P_1 & \defeq & P_1(q,a,w,b,q) & P_3 & \defeq & P_3(w,a,q,b,w)  \\
P_2 & \defeq & P_2(q,b,w,a,w) &P_4 & \defeq & P_4(w,b,q,a,q) 
\end{array}
\]
\noindent
and we put, as usual,
%$r_1 = \silent$, 
$r_5 = \mathit{cxt}$ and  $p_5 = \silent$.

@@

The encoding of the rules for reactions is  given in a parametric way:
\[
\begin{array}{lcl}
P_n(a,G,C,T) & \defeq &\pi_n(a,G,C,T).P_n(a,G,C,T)  \\
				&& +\\
			&&\sum_{x\in \{a,G,C\}} \pi'_n(x).P_n(a,G,C,T)
\end{array}
\]
where
\[
\begin{array}{lcl}
\pi_n(a,G,C,T) & \defeq & \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}
                                                    \chainedlink{G_i}{\noact}\chainedlink{\noact}{G_o}
                                                     \chainedlink{\overline{C}_i}{\noact}\chainedlink{\noact}{\overline{C}_o}
					        \chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}
					        \chainedlink{\widetilde{T}_i}{\noact}\chainedlink{\noact}{\widetilde{T}_o}
			\chainend{p_{n+1}}\\[6pt]
\pi'_n(x) &\defeq &  \startchain{r_n}\chainedlink{x_i}{\noact}\chainedlink{\noact}{x_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}} 
% \ + \   \startchain{r_n}\chainedlink{w_i}{\noact}\chainedlink{\noact}{w_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) \\
%			&&+\\
%			&& \startchain{r_n}\chainedlink{\overline{b}_i}{\noact}\chainedlink{\noact}{\overline{b}_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n}\chainend{p_{n+1}}.P_n(q,b,w,a,q) \ + \  \startchain{r_n}\chainedlink{a_i}{\noact}\chainedlink{\noact}{a_o}\chainedlink{r_{n+1}}{\noact}\chainedlink{\noact}{p_n} \chainend{p_{n+1}}.P_n(q,b,w,a,q) 
\end{array}
\]
\noindent
Then we have 
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl }
P_1 & \defeq & P_1(a,G,C,T) &   P_2 & \defeq & P_2(a,C,G,T') &   P_3 & \defeq & P_3(F,T,T',C)  \\
\end{array}
\]
\[
\begin{array}{lcl}
P_4 & \defeq &\startchain{r_4}\chainedlink{T'_i}{\noact}\chainedlink{\noact}{T'_o}
                                                     \chainedlink{\overline{F}_i}{\noact}\chainedlink{\noact}{\overline{F}_o}
					        \chainedlink{\mathit{cxt}}{\noact}\chainedlink{\noact}{p_4}
					        \chainedlink{\widetilde{G}_i}{\noact}\chainedlink{\noact}{\widetilde{G}_o}
			\chainend{\silent}.P_4  \\
				&& +\\
&&\startchain{r_4}\chainedlink{\overline{T'}_i}{\noact}\chainedlink{\noact}{\overline{T'}_o}\chainedlink{cxt}{\noact}\chainedlink{\noact}{p_4} \chainend{\silent}.P_4 \ +\  \startchain{r_4}\chainedlink{F_i}{\noact}\chainedlink{\noact}{F_o}\chainedlink{\mathit{cxt}}{\noact}\chainedlink{\noact}{p_4} \chainend{\silent}.P_4
\end{array}
\]
\noindent
%and we put $r_1 = \silent$.

@@

Here, the entities $T$ and $T'$ that can be produced by the reactions and that are not provided by the context:
\[
\begin{array}{lcllcl}
P (T,\widetilde{T})&\defeq & \sum_{h=0}^1 (\startchain{T_i}\chainedlink{T_o}{\noact}\chainend{\noact})^h\ \link{\widetilde{T}_i}{\widetilde{T}_o}.P (T,\widetilde{T})
& +  && \link{T_i}{T_o}.P (\overline{T},\widetilde{T}) \\
%\overline{P} (q)&\defeq &  \sum_{h=0}^1 (\startchain{\overline{T}_i}\chainedlink{\overline{T}_o}{\noact}\chainend{\noact})^h\link{\widetilde{T}_i}{\widetilde{T}_o}.P(q)\\
%&& + & && +\\
%&& \link{T_i}{T_o}.\overline{P}(T) &
%&& \link{\overline{T}_i}{\overline{T}_o}.\overline{P}(T)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl @{\hspace{0.5cm}}lcl}
P_T & \defeq & P(T,\widetilde{T})& \overline{P}_T & \defeq & P(\overline{T},\widetilde{T}) & P_{T'}& \defeq & P(T',\widetilde{T'}) & \\
\overline{P}_{T',\widetilde{T'}}& \defeq & P(\overline{T'},\widetilde{T'})\\\
\end{array}
\]
The entities that can be produced by the reactions and that can be  provided by the context are as follows:
\[
\begin{array}{lcl @{\hspace{1cm}}lcl}
P(C,\widehat{C},\underline{C},\widetilde{C}) & \defeq &  \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\widehat{C}_i}{\widehat{C}_o} (\startchain{\noact}\chainedlink{\noact}{\widetilde{C}_i}\chainend{\widetilde{C}_o})^h.   P(C,\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
&& \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o}.P(\overline{C},\widehat{C},\underline{C},\widetilde{C})\\
&&+\\
 && \sum_{h=0}^1 (\startchain{C_i}\chainedlink{C_o}{\noact}\chainend{\noact})^h\ \link{\underline{C}_i}{\underline{C}_o} \startchain{\noact}\chainedlink{\noact}{\widehat{C}_i}\chainend{\widehat{C}_o}.   P(C,\widehat{C},\underline{C},\widetilde{C}) \\
 %&  \overline{E} (a)&\defeq & \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\widehat{a}_i}{\widehat{a}_o}.E(a)\\
%&&  &  && +\\
%&& 
%&
%&& \sum_{h=1}^2 (\startchain{\overline{a}_i}\chainedlink{\overline{a}_o}{\noact}\chainend{\noact})^h\ \link{\underline{a}_i}{\underline{a}_o}.\overline{E}(q)\\
\end{array}
\]
Then, we have
\[
\begin{array}{lcl @{\hspace{1cm}}lcl@{\hspace{0.4cm}}lcl@{\hspace{0.4cm}}lcl}
P_C & \defeq &  P(C,\widehat{C},\underline{C},\widetilde{C})&  P_G& \defeq &   P(G,\widehat{G},\underline{G},\widetilde{G}) \\[6pt]
\overline{P}_C & \defeq &  P(\overline{C},\widehat{C},\underline{C},\widetilde{C}) & 
\overline{P}_G& \defeq &   P(\overline{G},\widehat{G},\underline{G},\widetilde{G})\\
\end{array}
\]

The encoding of the entity $F$ that can be provided by the context follows:
\[
\begin{array}{lcllcl}
P_F&\defeq & \sum_{h=0}^1 (\startchain{F_i}\chainedlink{F_o}{\noact}\chainend{\noact})^h\ \link{\widehat{F}_i}{\widehat{F}_o}.P_F
& +  && \sum_{h=0}^1 (\startchain{F_i}\chainedlink{F_o}{\noact}\chainend{\noact})^h. \link{\underline{F}_i}{\underline{F}_o}.\overline{P}_F \\[6pt]
\overline{P}_F&\defeq & \sum_{h=0}^1 (\startchain{\overline{F}_i}\chainedlink{\overline{F}_o}{\noact}\chainend{\noact})^h\ \link{\widehat{F}_i}{\widehat{F}_o}.P_F
& +  && \sum_{h=0}^1 (\startchain{\overline{F}_i}\chainedlink{\overline{F}_o}{\noact}\chainend{\noact})^h. \link{\underline{F}_i}{\underline{F}_o}.\overline{P}_F \\
%\overline{P} (q)&\defeq &  \sum_{h=0}^1 (\startchain{\overline{T}_i}\chainedlink{\overline{T}_o}{\noact}\chainend{\noact})^h\link{\widetilde{T}_i}{\widetilde{T}_o}.P(q)\\
%&& + & && +\\
%&& \link{T_i}{T_o}.\overline{P}(T) &
%&& \link{\overline{T}_i}{\overline{T}_o}.\overline{P}(T)\\
\end{array}
\]

### 2020-04-05 08-conclusion.tex
piccoli cambi

We believe that our embedding can contribute to extend the applications
of Reaction Systems to diverse fields of computer science, and life
sciences.
As we have already mentioned, the evolution of each process resulting from our embedding 
is deterministic, thus we do not have the problem of having infinitely many transitions
in the produced labelled transition system. In any case, we can exploit the implementation of  the symbolic semantics of the {\tt link}-calculus~\cite{BrodoO17} that can be found in~\cite{tool}.

As future work, we plan to implement a prototype of our framework,
with an automatic translation from RSs to  {\tt link}-calculus. 
We believe that our work can also help to extend the framework
of RSs towards a model which can improve the communication
between different RSs.

>>>>

We believe that our embedding can contribute to extend the applications
of Reaction Systems to diverse fields of computer science, and life
sciences.

As future work, we plan to implement a prototype of our framework,
with an automatic translation from RSs to  {\tt link}-calculus. 
We can also exploit the implementation of  the symbolic semantics of 
the {\tt link}-calculus~\cite{BrodoO17} that can be found in~\cite{tool}.

We believe that our work can also help to extend the framework
of RSs towards a model which can improve the communication
between different RSs.
